Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-07-09 snapshot_system/eval1.tex

We have implemented and evaluated a prototype of our VO scheme on a Linux cluster
of 8-core AMD FX-8120 at 3.1 GHz with 16 GB RAM. 
Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.
Each machine  is equiped with a 
a distributed file system (QFS) running in the cluster manages six 3TB disks
with default replication degree set to 3. The CDS replication is set to 5.
Objectives of our evaluation are:
1) Study the deduplicate detection and removal effectiveness of the VC approach and compare with an alternative VO
design.
2) Examine the impacts of VC for fault isolation and tolerance. 
3) Evaluate the backup throughput performance VC  for a large number of VMs.
4) Assess the resource usage  of VC in terms of memory, storage, and network bandwidth.
% the backup throughput performance VC  for a large number of VMs.
%Compare with the data domain approach~\cite{bottleneck08}.

@@

@@

{\bf Stateless Routing with Binning.}
We compare our system with Stateless Routing with Binning (SRB) in terms of
both backup time and deduplication efficiency. SRB is the same as the stateless
routing algorithm given in the Extreme Binning\cite{??} paper. the
deduplication efficiency is compared in
Figure~\ref{fig-exbin-efficiency-graph}, showing the deduplication efficiency
(percent of duplicate chunks which are deduped) of SRB and VC with several
different CDS sizes. From the graph you can see that VC provides similar or
better deduplication efficiency in all cases. In Figure~\ref{fig:srb_vs_vc} you
can see simulated backup times using actual throughput numbers from our test
backup cluster, and VC outperforms SRB mainly due to significantly fewer index
lookups (since SRB uses hash-partitioning, all lookups are essentially random
and caching will be largely innefective).  \emph{Should we use one of the two
bar charts, or the graph? I am thinking the graph, but I'll leave the two bar
charts in the paper until we decide? If we use the bar charts some text will
have to be changed. We could also add each of the CDS sizes to the bar chart
and have 4 bars instead of 2.}

@@

>>>>

We have implemented and evaluated a prototype of our VO scheme on a Linux cluster
of 8-core AMD FX-8120 at 3.1 GHz with 16 GB RAM. 
Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.
Each machine  is equipped with a 
a distributed file system (QFS) running in the cluster manages six 3TB disks
with default replication degree set to 3. The CDS replication is set to 5.
Objectives of our evaluation are:
1) Study the deduplicate detection and removal effectiveness of the VC approach and compare with an alternative VO
design.
2) Examine the impacts of VC for fault isolation and tolerance. 
3) Evaluate the backup throughput performance VC  for a large number of VMs.
4) Assess the resource usage  of VC in terms of memory, storage, and network bandwidth.
% the backup throughput performance VC  for a large number of VMs.
%Compare with the data domain approach~\cite{bottleneck08}.

@@

We will also compare our VC approach with  with
a VO approach  using stateless routing with binning (SRB).
SRB executes a distributed deduplication by routeing a data chunk to a machine~\cite{ParallelDataDomain}
using  the chunk hashing function discussed in \cite{??}. Within such a machine, the data chunk is compared with
a local index.

@@

%We assess the deduplication efficiency of VC and compare with
%that of an VO approach  using stateless routing with binning (SRB).
%SRB routes a data chunk to a machine~\cite{ParallelDataDomain}
%using  the chunk hashing function disussed in \cite{??}.

Figure~\ref{fig-exbin-efficiency-graph} shows the deduplication efficiency which is
the percent of deduped duplicate chunks by SRB and VC.
It also lists several PDS sizes chosen for VC. ``2\% PDS" means that
we allocate the space of distributed shared memory  to accommodate $\delta=2\%$
of data chunks shared among VMs. Namely 
With $\delta=2\%$, the deduplication efficiency can reach over 90\% 
while $\delta=4\%$, the deduplication efficiency can reach over 92\%. 
The loss of efficiency in VC is caused by the restriction of the total physical memory available
in the cluster to support PDS.  
The loss of efficiency in SRB is caused by the routing of data chunks which restricts the search scope
for global comparison.
In all cases, VC provides similar or better deduplication efficiency than SRB.

@@

In Figure~\ref{fig:srb_vs_vc} you
can see simulated backup times using actual throughput numbers from our test
backup cluster, and VC outperforms SRB mainly due to significantly fewer index
lookups (since SRB uses hash-partitioning, all lookups are essentially random
and caching will be largely innefective).  \emph{Should we use one of the two
bar charts, or the graph? I am thinking the graph, but I'll leave the two bar
charts in the paper until we decide? If we use the bar charts some text will
have to be changed. We could also add each of the CDS sizes to the bar chart
and have 4 bars instead of 2.}
